Assessing the Population-level Conservation Effects of Marine Protected Areas

### 2020-12-07 documents/pop-effects-of-mpas-front-matter.Rmd
Cb edits (#5)
* edits for revisions at Conservation Biology
* clean up and merge back to main

Co-authored-by: Owen Liu <owenrliu@gmail.com>

---
title: "Assessing the Population-level Conservation Effects of Marine Protected Areas"
subtitle: Cover Page
date: "`r Sys.Date()`"
output:
  bookdown::word_document2:
    reference_docx: uw.docx
  pdf_document: default
  word_document: default
---

## Article Impact Statement

Healthy marine ecosystems are critical to the well-being of the planet. Marine protected areas (MPAs) are increasingly being used to conserve and manage these ecosystems. We pair theory with empirical methods to show that the population-level conservation effects of marine protected areas can be highly variable and challenging to detect. We find no statistically clear effect of a large and well protected network of MPAs in the Channel Island, California, on targeted fin-fish after 14 years of protection, which we show is in fact to be expected. MPA practitioners must clearly communicate expectations from MPA networks, and plan monitoring and adaptations strategies that directly address the challenges of estimating population-level conservation effects of protected areas.

## Running Head

The Population Effects of MPAS

## Keywords:

@@

## Word Count

6000

## Author Details

@@

## Corresponding Author

Daniel Ovando
Fishery Science Building
University of Washington
1122 NE Boat Street, Seattle, WA 98195-5020 USA
danovan@uw.edu
phone: (805) 284 6864

## Acknowledgements

>>>>

---
output:
  bookdown::word_document2:
    reference_docx: template.docx
  pdf_document: default
  word_document: default
---

## Title  {.unnumbered}
Assessing the Population-level Conservation Effects of Marine Protected Areas

## Article Impact Statement {.unnumbered}

The population-level conservation effects of Marine Protected Areas are likely to be extremely challenging to detect

## Running Head {.unnumbered}

The Population-Level Effects of MPAS

## Keywords: {.unnumbered}

@@

## Word Count {.unnumbered}

5976

## Author Details {.unnumbered}

@@

## Corresponding Author  {.unnumbered}

Daniel Ovando
Fishery Science Building
University of Washington
1122 NE Boat Street, Seattle, WA 98195-5020 USA
danovan@uw.edu

## Acknowledgements  {.unnumbered}
